Monitoreo visual

### 2020-11-04 Ms_HabitatAves.Rmd
Archivo nuevo con tablas de ocupancia para sp simper
Mapas de prediccion de ocupancia para especies en invirnos y primavera. Primer plot

---
title: "Ms Habitat aves. Species composition in coastal urban habitats"
output:
  bookdown::word_document2:
    reference_docx: "Para_Template.docx"
bibliography: tesis_ref_2020.bib
---

@@

library(readxl)
library(tidyverse)
library(vegan)
library(MASS)
library(ggplot2)
library(ggrepel)
library(patchwork)
library(kableExtra)
library(knitr)

@@

[Provide general background information]
Urban modificacion over natural environments has promoted loss of native species and their replacement by non-native species [@mckinney2006urbanization]. This is called biotic homogenization, where few species are adapted to urban and suburban conditions [@mckinney1999biotic]. 
Biotic homogenization affects variety of ecosystems [grassland: @zeeman2017biotic], climates [temperate: @zeeman2017biotic],taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic]

[Stablish the importance of this research topic, more specific/detailed way]
This urban homogenization has effects: 
a. more homogenized biosfera with lower diversity, where there will be many species losers and few winners [@mckinney1999biotic].
which has been studied mostly in birds and plants

[Provide general background information, more specific/detailed way]
In birds, urban homogenization in more specific: has a nonrandom filtering effect on birds, they show guildsresponse to urbanization [@silva2016nonrandom].
Composición de aves urbanas depende más de la composición de aves urbanas aledañas que de los ambientes naturales que los rodean
Rural birds
According to @clergeau2001urban, urban  bird  communities  are  independent of the bird diversity of adjacent landscapes, and that local features are more important than surrounding landscapes.

@@

[Describe general problem area or the current research focus of the field]
half of population live in coastal cities, however urbanization has been msotly focus in terrestiral aspects.

@@

[General overview of this section]
In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, a Metropolitan area in Central Chile. We estimated species composition based on bird presence analised using occupancy models.

[Provide background information and justification]
Coastal central chile present a rapid urbanization growth since the last... years, endengering natural habitats. 
The area is near by the chilean capital which has close to 6 million inhabitants.
This area is inmerse ina a natural-rural matrix composed ... in a grographic Coastal mountain chain-- papers bahi concon y viña

[Provide an overview of the procedure/method itself]
species composition were analised with the package vegan for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models.

@@

```{r tabla3}
#Modelo 1= Abundancia ~ Estacion *Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
#Modelo 2= Abundancia ~ Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves )           #AIC 18241.0

@@

Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats. There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig. \@ref(fig:ANOSIM))

@@

There is just few species that contribute to differences between habitats. During winter: *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*. And spring: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*, according to simper analysis (Fig. \@ref(fig:SIMPER1), Fig. \@ref(fig:SIMPER2)).

```{r SIMPER1, fig.cap="Simper analysis for winter"}
# set pander table-layout options
library(pander)
Inv <-  read.csv("ResumenSimper_Inv2.csv")
Inv<- as.data.frame(Inv)
panderOptions('table.alignment.default', function(Inv)
    ifelse(sapply(Inv, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)

pander(Inv)
#Inv$Especie
```

```{r SIMPER2, fig.cap="Simper analysis for spring"}
# set pander table-layout options
library(pander)
Prim <-  read.csv("ResumenSimper_Prim2.csv")
Prim<- as.data.frame(Prim)
panderOptions('table.alignment.default', function(Prim)
    ifelse(sapply(Prim, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)

pander(Prim)

@@

species for each habitat
Occupancy model map show
```{r}
#ORDISTEP

@@

>>>>

---
title: "Bird species composition in coastal urban habitats"
output:
  bookdown::word_document2:
    reference_docx: "Para_Template.docx"
bibliography: tesis_ref_2020.bib
---

@@

library(readxl)
library(tidyverse)
library(vegan)
library(MASS)
library(ggplot2)
library(ggrepel)
library(patchwork)
library(kableExtra)
library(knitr)
library(rasterVis)

@@

[Provide general background information]
Urban modificacion over natural environments has promoted loss of native species and their replacement by non-native species [@mckinney2006urbanization]. This scenario shows how few species can adapt better to urban and suburban conditions [@mckinney1999biotic], however it affects to ecosystems [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic].

[Stablish the importance of this research topic, more specific/detailed way]
This urban homogenization is projected to lower diversity, where there will be many species losers and few winners [@mckinney1999biotic].
which has been studied mostly in birds and plants

[Provide general background information, more specific/detailed way]
Bird species comunnities in cities are more similar to urban communities nearby than to communities in sorroundinng natural environments. However, local features seems to be mportant in those assembles.
Composición de aves urbanas depende más de la composición de aves urbanas aledañas que de los ambientes naturales que los rodean
Rural birds
According to @clergeau2001urban, urban  bird  communities  are  independent of the bird diversity of adjacent landscapes, and that local features are more important than surrounding landscapes.

@@

[Describe general problem area or the current research focus of the field]
By 2019
half of population live in coastal cities, however urbanization has been msotly focus in terrestiral aspects.

@@

[General overview of this section]
In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, estimated species composition based on bird presence analised using occupancy models and analized bird assembles in those environment.

[Provide background information and justification]
The Gran Valparaíso, a Metropolitan coastal area in Central Chile, is formed by the conection of three cities: Valparaíso, a mayor port in the country, Viña del Mar, a big beach city since xxx and today one of the xx cities in ,  and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years. The area is near by the chilean capital, Santiago, which has close to 6 million inhabitants.
This area is inmerse ina a natural-rural matrix composed ... in a grographic Coastal mountain chain-- papers bahi concon y viña

[Provide an overview of the procedure/method itself]
To estimate species composition and assembles, occupancy models were developed with package DiversityOcuppancy [@divoccu] and 
species composition were analised with the package vegan [@Vegan] for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models.

@@

@@

Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats, this demonstrate that group of species for each habitat are different. There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig. \@ref(fig:ANOSIM))

@@

There is just few species that contribute to differences between habitats. During winter: *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*. And spring: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*, according to simper analysis (see Suplementary material for complete species list of SIMPER).

```{r OccuInv}
Pelecanus <-read_rds("PredInv_Pelecanus_thagus.rds")
Larus <-read_rds("PredInv_Larus_dominicanus.rds") 
Coragyps <-read_rds("PredInv_Coragyps_atratus.rds")
Larosterna <-read_rds("PredInv_Larosterna_inca.rds")
Leucophaeus <-read_rds("PredInv_Leucophaeus_modestus.rds")
Columba <-read_rds("PredInv_Columba_livia.rds")
Turdus <-read_rds("PredInv_Turdus_falcklandii.rds")
Sephanoides <-read_rds("PredInv_Sephanoides_sephaniodes.rds")

Especies <- stack(Pelecanus,Larus,Coragyps, Larosterna, Leucophaeus,  Columba, Turdus, Sephanoides)
names(Especies) <- c("Pelecanus thagus", "Larus dominicanus", "Coragyps atratus", "Larosterna inca", "Leucophaeus modestus", "Columba livia", "Turdus falcklandii", "Sephanoides sephaniodes")

Mytheme <- YlOrRdTheme()
Mytheme$panel.background$col <- "black"

levelplot(Especies, par.settings=Mytheme)

```{r OccuPrim}
Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
Larus <-read_rds("PredPrim_Larus_dominicanus.rds")
Columba <-read_rds("PredPrim_Columba_livia.rds")
Larosterna <-read_rds("PredPrim_Larosterna_inca.rds")
Phalacrocorax <-read_rds("PredPrim_Phalacrocorax_bougainvillii.rds")
Pelecanus <-read_rds("PredPrim_Pelecanus_thagus.rds")

Especies <- stack(Leucophaeus, Larus, Columba, Larosterna, Phalacrocorax,  Pelecanus)
names(Especies) <- c("Leucophaeus pipixcan", "Larus dominicanus", "Columba livia", "Larosterna inca", "Phalacrocorax bougainvillii", "Pelecanus thagus")

Mytheme <- YlOrRdTheme()
Mytheme$panel.background$col <- "black"

levelplot(Especies, par.settings=Mytheme)

@@

```{r}
#ORDISTEP

@@

species for each habitat
Occupancy model map show

```{r}
#Resultados occupancia para especies dde Simper
ModelosOccuPrim <- read_rds("ModelosOccuPrim_Ms.rds")
#Para generar las ecuaciones **Resultado_OccuPrim_Ms.rds** y **Resultado_OccuInv_Ms.rds**
```

### 2020-11-04 README.Rmd
Mapas de prediccion de ocupancia para especies en invirnos y primavera. Primer plot

>>>>

# Escritura manuscrito, arreglo de figuras y analisis especificos

Escritura de manuscrito en ingles **Ms_HabitatAves.Rmd**
El manuscrito cuenta con imput desde: 
- Algunos analisis ubicados en **Analisis_HabitatAves.R**. 
- Ocupancia de las especies obtenidas de simper para invierno y primavera en **Occu_especifica_Ms.R**, resultados en **Resultado_OccuPrim_Ms.rds** y **Resultado_OccuInv_Ms.rds**.
- En la segunda parte del script **Occu_especifica_Ms.R** se encuentra las predicciones realizadas para las especies seleccionadas antariormente, utilizando la capa **Capas_Proporcion_small.rds** creada desde los buffers y la altura. Cada especie (8 de invierno y6 de primavera) tienen sus resultados exportados por separado **PredEstacio_Especie.rds**
